{CPU-Scheduling}

### 2024-12-14 LaTeX/Sources/Advanced.tex
finished binary search

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{Assets/Ticket-Currency.pdf}
    \caption{Example of a Custom Ticket Currency}
    \label{fig:ticket-currencies}
\end{figure}

Another benefit comes with the ticket inflation or deflation operation, which can only be used by the owner of the currency.
This is the case, because it involves creating or destroying tickets. 
Still unlike the ticket transfer, ticket inflation does not need a sender and reciever.
The selected process just get more tickets assigned.
With this the parent process changes the ration of ownership and therefore boosts the selected job.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{Assets/Ticket-Currency.pdf}
    \caption{Example of a Custom Ticket Currency}
    \label{fig:ticket-currencies}
\end{figure}

Another benefit comes with custom currencies: the ticket inflation or deflation operation.
One needs a custom currency, because it involves creating or destroying tickets. 
Still unlike the ticket transfer, ticket inflation does not need a sender and reciever.
The selected process just get more tickets assigned.
With this the parent process changes the ration of ownership and therefore boosts the selected job.

\section{Lottery Scheduling}

Like other things in computer science the name already says a lot. 
Here randomization is exploited to achieve the proportianal share in runtime.
The concept that if even over a small scale there will be unavoidable errors, the longer the scheduler runs the more accurate the share becomes.
Think of the tickets as lottery tickets.
If the randomization is fair, than the more tickets you have the more you will win.
There is a downside though.
The randomizer algorithm can get pretty expensive.
There is a way to reuse one random seed though, but we will only quickly touch upon it later.
For an example implementation in C take a look at phd-mit-tr677.pdf (CITATION).

\subsection{Binary Search}

Basing the datastructure on a list is quite inefficient, because of the long search time.
Everytime you want to reschedule, you have to create a random number and loop through the list.
However you could use a balanced binary tree to make it much faster.
This is because a list search time scales with n. 
Therefore if you add one more element you will have to search through one more element.
In contrast a binary search scales not with n.
To be more precise it takes on $O(log(n))$ to find a specific value.
On average, with each decision we can eliminate half of the remaining candidates.
Therefore overall it is much faster, especially the more values the list contains.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{Assets/Binary-Search.pdf}
    \caption{Binary Search Example}
    \label{fig:binary-search}
\end{figure}

To understand it more, let's go through an example. Let's say there are 48 tickets and our winning one is 25.
To understand the decision better, feel free to look at figure \ref{fig:binary-search}.
For our first decision we need to choose if 25 is above 10 or not.
It is above ten, so we choose the right path.
At this point we have only 38 tickets left and we have to readjust our winning ticket.
We took away 10 tickets from the front so our new winning tickets is 15.
15 is smaller than 20, so we take a left turn and there is no readjusting needed.
In the next step we compare 12 and 15.
15 is larger, which means we take the right path and arrive at our winner process.
